Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-25 paper.tex
Updated Discussion
Work in progress.

@@

At some crucial moments during our research, we got the feeling we were doing
nature reverse engineering. One strategy was to let our imagination run wild
and go for the simple solution. One of our earlier experiment's findings was to
find balance, like the yin and yang, between death and reproduction.

In our experiments, we found that when solving simple problems, the cost of
communication between containers can become a factor to increase the total
performance time, even though, we believe that the opposite must also be true.
When solving complex problems, distributing the work on multiple resources
should reduce throughput time, making the communication cost negligible.

We must acknowledge the performance time of the DEAP library
\cite{fortin2012deap} is highly efficient and short, due in part because the
processing work execution is on a single processor with multiple cores, where
the communication time is nearly non-existent. In contrast, our algorithm
implementation requires a minimum of five containers and a message queue
server. Even though the container work has proven to be very effective and
efficient \cite{merelo2016performance,valdez2021container}, we must consider
some time was added to our experiments by the minimal delays (in the thousands
of a second magnitude) we used to keep the process execution relatively random,
to mimic how the life-cycle stages work in nature \cite{read1968system}. As
future work, we could test the Life-Cycle algorithm behavior by eliminating all
remaining delays.

This scheme allows for multiple parameter's fine tuning, granting us the
freedom to experiment with different selection and reproduction strategies
simultaneously, which will impact how fast it finds the solution and the
obtained quality.

@@

@@

>>>>

    Imagine being an astronaut on a mission repairing a space station in the
    middle of space. Suddenly, a block of asteroids hits the craft, and you
    lose your oxygen tank while the explosion pushes you away. From afar, you
    see the area where your tank might be, covered with something similar to a
    gas leaked from the station that blocks all visibility. Finding the tank is
    the only hope to return to your main ship some miles away. The oxygen
    reserve from your suit is running out, and there are only a couple of
    minutes left. Now hold your breath in real life and think, what strategy
    will you choose to search for your tank? We repeated this mental exercise
    several times until we found the best solution (or blacked out).

    If your life depended on it, would you choose a Genetic Algorithm, a
    variant of a Particle Swarm Optimization Algorithm, or another? We searched
    for a way to mix both, at least in some way, take the main idea or concepts
    from them and make them work together. We strongly believe it is possible
    to combine the features, as previous work has proven to obtain outstanding
    results \cite{garcia2015evospace,garcia2021event,valdez2021container,valdez2021swarm}.
    Our goal was to create a swarm out of the best individuals found in
    evolution. We probably have a long way to go, but at least we are getting
    promising results. From our experiments, all six Classic Benchmark
    Functions for Optimization (Ackley, Bohachevsky, Griewank, Rastrigin,
    Sphere, and Rosenbrock) proved the same behavior for the Animal Life Cycle
    Algorithm: finding the expected solution in a reduced number of evaluations
    and less execution time.

@@

@@

%At some crucial moments during our research, we got the feeling we were doing nature reverse engineering. One strategy was to let our imagination run wild and go for the simple solution. One of our earlier experiment's findings was to find balance, like the yin and yang, between death and reproduction.
%In our experiments, we found that when solving simple problems, the cost of communication between containers can become a factor to increase the total performance time, even though, we believe that the opposite must also be true. When solving complex problems, distributing the work on multiple resources should reduce throughput time, making the communication cost negligible.
%We must acknowledge the performance time of the DEAP library \cite{fortin2012deap} is highly efficient and short, due in part because the processing work execution is on a single processor with multiple cores, where the communication time is nearly non-existent. In contrast, our algorithm implementation requires a minimum of five containers and a message queue server. Even though the container work has proven to be very effective and efficient \cite{merelo2016performance,valdez2021container}, we must consider some time was added to our experiments by the minimal delays (in the thousands of a second magnitude) we used to keep the process execution relatively random, to mimic how the life-cycle stages work in nature \cite{read1968system}. 
%This scheme allows for multiple parameter's fine tuning, granting us the freedom to experiment with different selection and reproduction strategies simultaneously, which will impact how fast it finds the solution and the obtained quality. 
%As future work, we could test the Life-Cycle algorithm behavior by eliminating all remaining delays.

@@

%---------------------------------------------------- garcia2015evospace  garcia2021event  valdez2021container  valdez2021swarm
